---
title: "Convert a spectral reference library with dialects"
author: "Madeleine J Otway"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ConvertSRL}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo = F, message = F, warning = F}
library(dialects)
library(knitr)
library(kableExtra)
```
```{r}
library(dialects)
library(knitr)
library(kableExtra)
```

## Import a fasta file

The user must first download a protein sequence database in fasta format (available at www.uniprot.org/). This function will work with SwissProt and TrEMBL formatted protein sequences. The user can then import the fasta file into the global environmet.

```{r}
human.proteome <- import.fasta(system.file("extdata", "human_proteome_example.fasta", package = "dialects"))
```
```{r echo = FALSE, results = 'asis'}
kable(head(human.proteome), format = "html") %>%
  scroll_box(width = "688px", height = "300px")
```


## Digest the fasta file

The user then performs an in silico trypsin digestion. This diestion does not moodel Lys-C and does not include missed cleavages.

```{r}
digest.human <- digest.fasta(human.proteome)
```
```{r echo = FALSE, results = 'asis'}
kable(head(digest.human), format = "html") %>%
  scroll_box(width = "688px", height = "300px")
```


## Import a spectral reference library (SRL)

The user can then import an SRL into the global environment. This package is compatable with either PeakView/OneOmics or OpenSWATH SRL format. NOTE: This package cannot convert between PeakView/OneOmics and OpenSWATH formats. Also note: OpenSWATH format must be comma separated.

```{r}
rat.srl <- import.srl(system.file("extdata", "rat_srl_example.txt", package = "dialects"), SRL.format = "peakview")
```
```{r echo = FALSE, results = 'asis'}
kable((rat.srl), format = "html") %>%
  scroll_box(width = "688px", height = "300px")
```


## Covert the species of the SRL

Users will convert the species of the SRL to that of the fasta file, where full sequence identity occurs. NOTE: All retention time calibration peptides will not be converted and will not be copied to the new SRL. 

```{r}
human.from.rat <- convert.species(rat.srl, digest.human)
```
```{r echo = FALSE, results = 'asis'}
kable(head(human.from.rat), format = "html") %>%
  scroll_box(width = "688px", height = "300px")
```


## Covert the species of the SRL

Users export the SRL in either PeakView/OneOmics or OpenSWATH format. The format of the imported and exported SRL will be identical. A PeakView/OneOmics SRL will be tab separated and an OpenSWATH SRL will be comma separated.

```{r}
# export.srl(human.from.rat, system.file("extdata", "human-from-rat-srl.txt", package = "dialects"))
```


## Session info
```{r}
sessionInfo()
```


